---
title: "Analysis of cyber security Video Stats"
author: "Siddharthan"
date: "30/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

# Introduction

There is an increase in career demand for the candidates who have specialization in the cyber security. Due to these unprecended times most of the Universities have decided to make the course available via online sessions. Since the course is delivered via online, there might be some difficulties which could be faced by both the learners and the professors who are handling the modules. In order to make the online sessions a fabulous and to make the learners get used to it as like they can view the course materials whenever they want which helps them to go through whenever they find some issue. These online activities are recorded in order to improve the course handling. The online activities of enrolments, survey response, leaving survey response, question response, step activity and statistics of viewing the videos are recorded and stored in the Future Learn MOOC dataset

The observations made on these data are captured based on different simulations on a particular period of time. This report consists of a analysis that is made on the statistics of viewing the videos. The data consists of various responses of different course modules like video duration, total views of the courses, views based on the regions, views based on the hardware devices and much more. With these responses an exploratory data analysis is made up with some numerical and graphical summaries. 

# Analysis

Before proceeding with the analysis, the data is inspected to verify whether the structure of the data is good for analysis and whether the data has unknown values in some of the responses. These unknown values are removed based on the data cleaning process and the structure is also changed for the columns which are required for analysis. 

Some assumptions are made which were missing in the dataset such as the year and month at which the responses were recorded. These two columns where inserted into the dataset and they are used in the analysis process. Since there were less observations, two datafiles have been used in the analysis process and these two files where combined and stored as a dataframe.

```{r include=FALSE}
#Load the project
library('ProjectTemplate')
load.project()
#Execute the analysis file
source("src/Analysis.R")
```

## Numerical Analysis

The data mainly consists of values encoded as quantitative variables. The first approach to analysis the data based on the numerical process is to summarize the dataset inorder to get the central tendancy. It can be done by calling the summary() function over the dataset. Here the central tendancy is calculated for set of responses which would be easy for analysing.


```{r echo=TRUE}
summary(video_stats_data[,21:26])
```

* The central tendancy is calculated for the responses that are recorded based on the regions. 

* While looking at this we can consider that majority of the courses are viewed highly from the Europe region rather than the other region. 

* The maximum view percentage from the Europe region 67.25 where as the courses are viewed less in the South America region.

* Further to our analysis we can try to find is there any correlation between the responses recorded. To compute the correlation matrix the cor() function can be used. 

* The correlation between different responses establishes that many responses are correlated to each other. 

* We could find that the total_downloads response is highly correlated with transcript_views response of **0.9409151**

```{r echo=TRUE}
cor(video_stats_data[,5], video_stats_data[,7])
```

* The index 5 and 7 from the code represents the two responses total_downloads abd total_transcript_views respectively. 

* From this, its applicable to represent that the courses that are downloaded mostly as a transcript type. With this numerical summaries, the data can be further analysed graphically.

## Graphical Analysis

The graphical analysis is made with line graphs, points and bar plots, which helps to visualize and interpret the data. The **ggplot2** library is used for this graphical analysis.

\newpage
**Graphical representation 1 :**

```{r Bar Plot1, echo=FALSE, fig.height=4, fig.width=7}
plot1
```

* This plot graphically explains that there is a certain amount of increase in views to the latter month which is *November* compared to that of the previous month *September*. 

* The modules has made some significant impact with the leaners and this made a growth in the trend  of viewers. 

* The modules which are viewed in less numbers were also made an impact the following month with the increase in the viewers.

\newpage
**Graphical representation 2 :**

```{r Bar Plot2, echo=FALSE, fig.height=4, fig.width=7}
plot2
```

* The above bar plot represents the analysis made based on the modeules that are viewed ***100%*** from the Asia region. 

* From this graph its easy to interpret that above **60%** of the learners have viewed most of the modules completely. 

* And below **40%** of the learners have viewed two or three modules completely. This suggests that the learners are not interested in viewing those modules as it maybe out of the scope. 

* Approximately around **50% - 60%** of the learners are completing the modules which they find it covers their necessity.

\newpage
**Graphical representation 3 :**

```{r Point Plot1, echo=FALSE, fig.height=4, fig.width=7}
plot3
```

* From the plot, its significantly visible that the module did not made a much impact in the Europe region learners as the view percentage critically dropped during the **November** month compared to the month of **September**. 

* The lightly shaded points shows that the video duration is less than 100 minutes and the dark shaded points shows the video duration is more than 400 minutes.

**Graphical representation 4 :**

```{r Line Graph1, echo=FALSE, fig.height=3.5, fig.width=7}
plot4
```

* Its obvious that the learners from the North American region have lost their interest in the modules as it clearly shows a depletion in the view percentage in the **November** month.

* This sums up that the learners started downloading the contents of the modules rather than viewing the materials online.

**Graphical representation 5 :**

```{r Point Plot2, echo=FALSE, fig.height=4, fig.width=7}
plot5
```

* The representation is based on the analysis made on the modules that are viewed using the desktop devices. 

* Based on the total views of the modules, the points represent that the learners viewed through the desktop devices for most important topics, whereas there is a shrinkage in desktop views for the courses which has less viewers.

\newpage
**Graphical representation 6 :**

```{r Point Plot3, echo=FALSE, fig.height=4, fig.width=7}
plot6
```

* From this graph, it obvious that only one module is downloaded and viewed in hd format by most of the learners. 

* This suggests that the learners had an impact from that particular module as we can assume it was predominantly used in their work environment.

**Graphical representation 7 :**

```{r Bar Chart, echo=FALSE, fig.height=4, fig.width=7}
plot7
```

* This bar chart clearly shows that there is an increase in course downloads in later month compared to that of the previous month. 

* This clearly represents that the learners are interested in the contents of the course and they downloaded the contents for further usage purposes. 

* There was no depletion in any course that was being downloaded compared to the previous month.

**Graphical representation 8 :**

```{r Line Graph2, echo=FALSE, fig.height=4, fig.width=7}
plot8

```

* As observed in the numerical summaries that there is huge correlation between the total_downloads and transcription views, this line plot clearly shows that in both months, maximum of the course materials are downloaded as the transcripts. 

* And in the month of **November** the materials that are downloaded as the transcript view has increased to the peak.

# Reproducibility

* Project Template is used to pre-process the data, compute the necessary functions mentioned and then generate the report through the Rmarkdown.

* If there is a new file which is required to generate the report, it should be inserted in the data directory and it should contain the same variable names as mentioned in the report to avoid further errors.

* For the purpose of analysis the datasets are combined as a single dataframe and hence if there is any news files which should be reported, it needs to be manually update the pre-process file to combine the data which would be in the munge sub directory.

* The analysis of the report is not completely reproducible as some manual interventions are required to change the variable names, binding up of the datasets as a single dataframe when there appears a new datafile.

* Apart from this, the report will be automatically generated when it is made to run from the R markdown report file which is in the Report sub directory.

# Conclusion

After a brief analysis of the data set available, it can be said that the course modules are quite engaging for the learners considering the number of downloads of the course materials. This depicts that the learners want to use it for reference later or share with other people. The length of video however, at times makes the content lose it’s appeal on the viewers and they tend to not finish the course till the very end. More information about the leaving responses of such learner can be gained through the leaving response surveys conducted which is out of the scope of this analysis.